\Trill: Secure firewall-traversing networking

### 2012-11-12 6.858/proposal/proposal.tex
Formatted some things

\usepackage{geometry, xspace}
\usepackage[parfill]{parskip}
\geometry{letterpaper}

\newcommand{\trill}{\textsc{Trill}\xspace}

\title{Trill: Secure firewall-traversing networking}
\author{Carl Jackson and Max Wang}
\date{November 5, 2012}

@@

\section*{Overview}
We propose to design and implement \trill, a networking abstraction that
provides secure communication between federated identities, either of which
could be behind a firewall.

>>>>

\usepackage{fancyhdr, geometry, xspace}
\usepackage[parfill]{parskip}
\geometry{letterpaper,text={7in,9in},centering}
\pagestyle{fancy}

\newcommand{\Trill}{\textsc{Trill}\xspace}

\title{\Trill: Secure firewall-traversing networking}
\author{Carl Jackson and Max Wang}
\date{November 5, 2012}

\makeatletter
\renewcommand{\maketitle}{%
  \thispagestyle{plain}%
  \begin{center}%
    {\LARGE \@title \par}%
    {\large \@author \par}%
    {\large \@date \par}%
  \end{center}%
}
\makeatother

@@

\section*{Overview}
We propose to design and implement \Trill, a networking abstraction that
provides secure communication between federated identities, either of which
could be behind a firewall.
